Models of Lambek calculus with subexponentials

### 2019-06-03 PaperDraft.tex
representation theorem

\theoremstyle{col}
\newtheorem{col}{Corollary}
\usepackage{listings} 		% for source code
\date{}
\author[1,2]{Daniel Rogozin}
\affil[1]{Lomonosov Moscow State University}
\affil[2]{Serokell O\"{U}}
\title{Models of Lambek calculus with subexponentials}

@@

So, $\hat{\Box} \theta(a) = \theta(\Box_{\mathcal{S}} a)$.

@@

@@

\begin{center}
  $A \backslash B = \{ C \: | \: A \circ C \leq B \}$

@@

Author would like to thank Lev Beklemishev, Stepan Kuznetsov, Fedor Pakhomov, Danyar Shamkanov, and Andre Scedrov
for advice, critics, and comments.

>>>>

\theoremstyle{col}
\newtheorem{col}{Corollary}
\usepackage{listings} 		% for source code
\date{}
\author[1,2]{Danya Rogozin}
\affil[1]{Lomonosov Moscow State University}
\affil[2]{Serokell O\"{U}}
\title{Models of Lambek calculus with subexponentials}

@@

Thus, $\hat{\Box} \theta(a) = \theta(\Box_{\mathcal{S}} a)$.

@@

\begin{theorem}
  Let $\mathfrak{Q} = \langle \mathcal{Q}, I \rangle$ be a quantale with
  quantic conucleus. Then $\mathfrak{Q}$ is isomorphic to relational quantale on $Q$ with some quantic conucleus.
\end{theorem}

\begin{proof}
  Let $I$ be a quantic conucleus. Then $\mathcal{Q}_{I} = \{ a \in \mathcal{Q} \: | \: I(a) = a \}$ is a subquantale of $\mathcal{Q}$.

  Let us define $I'(a) = \bigvee \{ s \in \mathcal{Q}_{I} \: | \: s \leq a \}$.

  It is clear that $I'$ is a quantic conucleus. Let us show that for all
  $a \in \mathcal{Q}$ $I(a) = I'(a)$.

  $\begin{array}{lll}
  & I'(a) = \bigvee \{ s \in \mathcal{Q}_{I} \: | \: s \leq a \} = & \\
  & \bigvee \{ s \in \mathcal{Q}_{I} \: | \: I(s) \leq a \} = & \\
  & \bigvee \{ s \in \mathcal{Q}_{I} \: | \: I(s) \leq I(a) \} \leq I(a)&
  \end{array}$

  It is clear that, $I(a) \leq a$. So $I(a) \leq \bigvee \{ s \in \mathcal{Q}_{I} \: | \: s \leq a \} = I'(a)$.

  Thus, we showed that $I(a) = I'(a)$. One need to apply the previous theorem with $I'$.
\end{proof}

@@

\begin{center}
  $A \backslash B = \bigvee \{ C \: | \: A \circ C \leq B \}$

@@

Author would like to thank Lev Beklemishev, Stepan Kuznetsov, Fedor Pakhomov, Danyar Shamkanov, and Andre Scedrov
for advice, critique, and comments.
